Supporting Ecological Decision Making Using Feature-Selection and Variable Importance

### 2019-08-31 code/98-paper/ieee/ieee-manuscript.tex
add jose as author, - add notes to discussion section

\author{Patrick~Schratz,~\IEEEmembership{Member,~IEEE,}
        Jannes~Muenchow,~\IEEEmembership{Member,~IEEE,}
        Eugenia Iturritxa,~\IEEEmembership{Member,~IEEE,}
        Bernd~Bischl,~\IEEEmembership{Member,~IEEE,}
        and Alexander~Brenning,~\IEEEmembership{Member,~IEEE}
\thanks{P. Schratz, J. Muenchow and A. Brenning are with the Department
of Geography, GIScience group, Friedrich-Schiller-University of Jena, Germany.}% <-this % stops a space
\thanks{B. Bischl is head of the computational statistics group at the Department of Statistics, Ludwig-Maximilian-University Munich.}% <-this % stops a space
\thanks{E. Iturritxa is with NEIKER Tecnalia, Vitoria-Gasteiz, Arab, Spain.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}
}

@@

The magniute of bias introduced by these facts cannot be quantified.
However, it has to be considered when making interpretations about the outcome of this study.

@@

@@

>>>>

\author{Patrick~Schratz,~\IEEEmembership{Member,~IEEE,}
        Jannes~Muenchow,~\IEEEmembership{Member,~IEEE,}
        Eugenia Iturritxa,~\IEEEmembership{Member,~IEEE,}
        José Cortés, ~\IEEEmembership{Member,~IEEE,}
        Bernd~Bischl,~\IEEEmembership{Member,~IEEE,}
        and Alexander~Brenning,~\IEEEmembership{Member,~IEEE}
\thanks{P. Schratz, J. Muenchow, J. Cortés and A. Brenning are with the Department
of Geography, GIScience group, Friedrich-Schiller-University of Jena, Germany.}% <-this % stops a space
\thanks{B. Bischl is head of the computational statistics group at the Department of Statistics, Ludwig-Maximilian-University Munich.}% <-this % stops a space
\thanks{E. Iturritxa is with NEIKER Tecnalia, Vitoria-Gasteiz, Arab, Spain.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}
}

@@

The magnitude of bias introduced by these facts cannot be quantified.
However, it has to be considered when making interpretations about the outcome of this study.

@@

% - Ensemble FS show no advantage to simple methods -> maybe to less features, features too correlated? check diff between effect on NRI and VI
% - Effect varies across learnes -> suggest to use FS even on feature sets with p < 100?
% - When calculating multiple filters, consider to only use ensemble filter?
% - PCA shows similar performance but probably requires tuning of main components -> check runtime!

@@

WIP
